---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# xkcd

<!-- badges: start -->
<!-- badges: end -->

The `xkcd` package provides an R interface to retrieve data about [xkcd comics](https://xkcd.com) using the xkcd [JSON API](https://xkcd.com/json.html). Most importantly, you can display these comics in the RStudio plot window.

## Installation

You can install the development version of xkcd from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("yaridmd/xkcd")
```

## Usage

Given an xkcd number, the `xkcd()` function returns a list object with metadata about the comic.

```{r example}
library(xkcd)

first_comic <- xkcd(1)
print(first_comic)
```

The `draw_comic()` function takes in this list of metadata, and displays the actual comic strip image in the plot window:

